### 2014-12-09 paper.tex
minor updates, updated code

  Overall, the voter share/seat share metric is much easier to calculate, as nothing needs to be known about the individual districts, but rather the totals of the overall election.  However, as we will expose in the analysis and discussion sections, the assumption that all districts have the same total votes is wrong due to turnout variance and creates issues when analyzing the data.\\

@@

  \subsection{Court Test Threshold}
  10\% for areas w/at least 3 districts
  \subsection{Policy Recommendations}
  Use nonpartisan methods

>>>>

  Overall, the voter share/seat share metric is much easier to calculate, as nothing needs to be known about the individual districts, but rather only the totals of the overall election.  However, as we will expose in the analysis and discussion sections, the assumption that all districts have the same total votes does not hold well due to turnout variance and creates issues when analyzing the data.\\

@@

  \subsection{Court Test Threshold}
  10\% for areas w/at least 3 districts, include compactness considerations.  if close on one, consider the other
  \subsection{Policy Recommendations}
  Use nonpartisan methods
